Julkaisutoiminta Vaasassa 1764-1917

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa, osa 4

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mar=c(8,8,5,3))
plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.5,xlab="vuosi",ylab="dokumenttia",cex.axis=2,axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="grey",lwd=2.5)
axis(side = 1, at = c(1764,1809,1863,1917))
axis(side = 2, at = c(0,25,50,75,100,125,150,175,194))
```

>>>>

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(6,2,0))
par(mar=c(8,8,5,3))
plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.4,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="darkgrey",lwd=4)
axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3.2)
axis(side = 2, at = c(0,20,40,60,80,100,120,140,160,180,194),cex.axis=2.4)
```

```{r, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(6,2,0))
par(mar=c(8,8,5,3))
plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.4,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="darkgrey",lwd=4)
axis(side = 1, at = c(1764,1780,1800,1820,1840,1860,1880,1900,1917),cex.axis=3.2)
axis(side = 2, at = c(0,20,40,60,80,100,120,140,160,180,194),cex.axis=2.4)
```
